DisReserv (v1.0): Analytical displacement solution due to reservoir compaction with arbitrary geometry and under arbitrary pressure changes

### 2020-09-19 manuscript/manuscript-reservoir.tex
define Nagy solution for jth prism (eqs 25-28)

From the potential theory, a particular solution of equation \ref{eq:poisson} is
\begin{equation}
\phi(x,y,z) = -  \frac{m}{4 \pi} \int\int\limits_{v}\int \frac{T(x^{\prime}, y^{\prime}, z^{\prime} )}{\sqrt{(x - x^{\prime})^{2} + (y - y^{\prime})^{2} + (z - z^{\prime})^{2}}} \: dv,
\label{eq:phi}
\end{equation}
where $\phi(x,y,z)$ represents the Newtonian gravitational potential \citep{Kellogg29} that would be produced at the coordinates $x, y$ and $z$ by a continuous density distribution $- \frac{m}{4 \pi}  \: T( x^{\prime}, y^{\prime}, z^{\prime} )$. 
The integral in equation \ref{eq:phi} is conducted over the coordinates $x^{\prime}$,$y^{\prime}$ and $z^{\prime}$, denoting, respectively, the $x-$, $y-$ and $-z$ coordinates of an arbitrary point belonging to the interior of the volume $v$ of the solid.

@@

\: \Delta p_{j} \: \:dv_j

@@

\phi_{1} = - \frac{C_m}{4 \pi}  \frac{\Delta p_{j} \: \:dv_j}{ {R_1}_{ij} } \: .

@@

\bigg]   \: \Delta p_{j}  \:dv_j

@@

\phi_{2} = - \frac{C_m}{4 \pi}  \frac{\Delta p_{j} \: \:dv_j}{ {R_2}_{ij} } \: .

@@

$\Delta p_j$  is the pressure contrast of the $j$th nucleus, $dv_j$ is an 
infinitesimal element of volume of the $j$th nucleus, $A$ is the constant

@@

\: \Delta p_{j} \: \:dv_j \: .

@@

By following \cite{Sharma56} and \cite{Tempone10}, 
the stress vector 
$\mbox{\boldmath$\sigma$}_{ij} \equiv \mbox{\boldmath$\sigma$}(x_{i}, y_{i}, z_{i}, x^{\prime}_{j}, y^{\prime}_{j}, z^{\prime}_{j})$ 
at the point $(x_{i}, y_{i}, z_{i})$ due to the $j$th single nucleus of strain buried 
in the half space is given by
\begin{equation}
\mbox{\boldmath$\sigma$}_{ij} = \mbox{\boldmath$\sigma_{1}$}_{ij} + 
\mbox{\boldmath$\sigma_{2}$}_{ij} \: ,
\label{eq:stress_nucleus}
\end{equation}
where 
$\mbox{\boldmath$\sigma_{1}$}_{ij} \equiv \mbox{\boldmath$\sigma_{1}$}(x_{i}, y_{i}, z_{i}, x^{\prime}_{j}, y^{\prime}_{j}, z^{\prime}_{j})$ is the stress vector 
at the point $(x_{i}, y_{i}, z_{i})$ due to the $j$th single nucleus in the infinite space and $\mbox{\boldmath$\sigma_{2}$}_{ij} \equiv \mbox{\boldmath$\sigma_{2}$}(x_{i}, y_{i}, z_{i}, x^{\prime}_{j}, y^{\prime}_{j}, z^{\prime}_{j})$ is the stress vector 
at the point $(x_{i}, y_{i}, z_{i})$ that gives the correction of the stress due to the 
$j$th image nucleus considering a semi-space. These two vectors are given by
\begin{equation}
\mbox{\boldmath$\sigma_{1}$}_{ij} =
A  \: 
\begin{bmatrix} 
\frac{\partial^{2} }{\partial x \partial z} {\frac{1}{{R_1}_{ij}}}  \\
\frac{\partial^{2} }{\partial y \partial z} {\frac{1}{{R_1}_{ij}}}  \\
\frac{\partial^{2} }{\partial z^{2}} {\frac{1}{{R_1}_{ij}}} 
\end{bmatrix}
\: \Delta p_{j} \: \:dv_j \: ,
\label{eq:nucleus-stress1-vector}
\end{equation}
and 
\begin{equation}
\mbox{\boldmath$\sigma_{2}$}_{ij} = 
A  \: 
\left\{
\begin{bmatrix} 
\frac{\partial^{2}  }{\partial x \partial z} {\frac{1}{{R_2}_{ij}}} \\
\frac{\partial^{2} }{\partial y \partial z} {\frac{1}{{R_2}_{ij}}} \\
- \frac{\partial^{2} }{\partial z^{2}} {\frac{1}{{R_2}_{ij}}}   
\end{bmatrix}
+ 2 \: z_{i}
\begin{bmatrix} 
\frac{\partial^{3}  }{\partial x \partial z^{2}} {\frac{1}{{R_2}_{ij}}} \\
\frac{\partial^{3} }{\partial y \partial z^{2}} {\frac{1}{{R_2}_{ij}}} \\
\frac{\partial^{3} }{\partial z^{3}} {\frac{1}{{R_2}_{ij}}} 
\end{bmatrix}
\right\}
\: \Delta p_{j} \: \:dv_j \: .
\label{eq:nucleus-stress2-vector}
\end{equation}
According to \cite{Sharma56} and \cite{Tempone10}, the Beltrami’s equations \citep{Beltrami} and the equilibrium equations must be satisfied to obtain the contribution of the stress field in the half space. 
Additionally, the following boundary conditions at the free surface ($z_i = 0$) 
must be satisfied
\begin{equation}
\mbox{\boldmath$\sigma$}_{ij} = \mbox{\boldmath$\sigma_{1}$}_{ij} + 
\mbox{\boldmath$\sigma_{2}$}_{ij} = \mbox{ \boldmath$0$},
\label{eq:null_stress}
\end{equation}
where $\mbox{ \boldmath$0$}$ is the null vector.
This condition can be easily verified by adding the vectors 
$\mbox{\boldmath$\sigma_{1}$}_{ij}$ (equation \ref{eq:nucleus-stress1-vector}) and 
$\mbox{\boldmath$\sigma_{2}$}_{ij}$ (equation \ref{eq:nucleus-stress2-vector}) 
computed at any point on the free surface $(x_i, y_i, z_i = 0)$.

@@

We parameterize the reservoir as a grid of juxtaposed right rectangular prisms.
Each grid prism has a constant pressure contrast $\Delta p_{j}$; however, pressure variations among different prisms are allowed. 
To calculate the displacement field produced by the $jth$ prism
at the $i$th coordinates  $(x_i$, $y_i, z_i)$, we integrate the solution deduced for a single nucleus of strain (equation \ref{eq:displacement_ui})
over its volume and obtain
\begin{equation}
{\bf{\tilde{u}}}_{ij} = 
\int_{z_1}^{z_2} \:\:
\int_{y_1}^{y_2} \:\: 
\int_{x_1}^{x_2} 
{\bf{u_{1}}}_{ij} \: \:  dx^{\prime}_j dy^{\prime}_j dz^{\prime}_j 
\: + \:
\int_{z_1 - 2 \, z_c}^{z_2 - 2 \, z_c} \:\:
\int_{y_1}^{y_2} \:\: 
\int_{x_1}^{x_2} 
{\bf{u_{2}}}_{ij} \:\:  dx^{\prime}_j dy^{\prime}_j dz^{\prime}_j \: ,
\label{eq:nucleus-ui_jth_prism}
\end{equation}
where the limits of the integrals are defined by the borders and the center 
of the $j$th prism in the following way: $x_1$ and $x_2$ are their south and north borders; $y_1$ and  $y_2$ are their  west and east borders; $z_1$ and $z_2$ are their depths to the top and bottom; and $z_c = \frac{1}{2}(z_1 + z_2)$ is its center depth. 
In equation \ref{eq:nucleus-ui_jth_prism}, the integrations are conducted with respect to the variables $(x^{\prime}_{j}, y^{\prime}_{j}, z^{\prime}_{j})$. 
The integral depending on ${\bf{u_{1}}}_{ij}$,
the displacement field due to a single nucleus in the infinite space (equations \ref{eq:nucleus-u1} and  \ref{eq:nucleus-u1-vector}), is conducted over the volume of the $j$th prism. The integral depending on ${\bf{u_{2}}}_{ij}$,
the displacement field due to the image nucleus (equations \ref{eq:nucleus-u2} and  \ref{eq:nucleus-u2-vector}), is conducted over the volume of a different prism
symmetrically positioned above the free surface and conveniently called "image prism".

By substituting equations \ref{eq:nucleus-u1-vector} and \ref{eq:nucleus-u2-vector} into equation \ref{eq:nucleus-ui_jth_prism}, we obtain the components of the displacement vector ${\bf{\tilde{u}}}_{ij}$ due to the pressure change in the $j$th prism, i.e.:
\begin{equation}
{\tilde{u}}_{{ij}_\alpha} = \frac{A  \: (1 + \nu)}{E} 
\: \Delta p_{j}  \: \left[ \int\int\limits_{v_j}\int 
\frac{\partial }{\partial \alpha} {\frac{1}{{R_1}_{ij}}} \:  dv_j 
\: + \: 
(3  - 4 \nu)  \int\int\limits_{v_j}\int
\: \frac{\partial }{\partial \alpha} {\frac{1}{{R_2}_{ij}}}\:  dv_j
+ \: 2 \: z_{i} \:  \int\int\limits_{v_j}\int
\frac{\partial^{2}  }{\partial \alpha \partial z} {\frac{1}{{R_2}_{ij}}}  \:\:  dv_j 
\right] \: , 
\label{eq:u_til_alpha}
\end{equation}
and
\begin{equation}
{\tilde{u}}_{{ij}_z} = \frac{A  \: (1 + \nu)}{E} 
\: \Delta p_{j}  \: \left[ \int\int\limits_{v_j}\int 
\frac{\partial }{\partial z} {\frac{1}{{R_1}_{ij}}} \:  dv_j 
\: - \: (3  - 4 \nu)  \int\int\limits_{v_j}\int
\: \frac{\partial }{\partial z} {\frac{1}{{R_2}_{ij}}}\:  dv_j
+ \: 2 \: z_{i} \:  \int\int\limits_{v_j}\int
\frac{\partial^{2}  }{\partial z^{2}} {\frac{1}{{R_2}_{ij}}}  \:\:  dv_j 
\right] \: , 
\label{eq:u_til_z}
\end{equation}
where $\alpha = x, y$ and $dv_j$ is the $j$th element of volume of the $j$th prism 
whose volume is $v_j$.
In the right-hand side of equations \ref{eq:u_til_alpha} and \ref{eq:u_til_z}, the three integrals have the same form of derivatives of the gravitational field produced by the 
$j$th prism. 
The first integral corresponds to the $\alpha-$component of the gravitational attraction 
produced by the $j$th prism.
The second and third integrals correspond, respectively, to the $\alpha-$component of the gravitational attraction and to the $\alpha \:z-$component of the gravitational 
gradient tensor produced by the $j$th image prism. 
The similarity between the displacement fields due to a volume source in a half-space and the gravitational field allows the use of closed expressions of the gravitational potential and its derivatives produced by the 3D right rectangular prism derived by \cite{Nagyetal2000} and (\citeyear{Nagyetal2002}).

@@

The first integral in the right-hand side of equations  \ref{eq:u_til_alpha} and \ref{eq:u_til_z}  is the first derivatives of ${\frac{1}{{R_1}_{ij}}}$ with respect to $x$, $y$ and $z$ which are, respectively, given by the following closed expressions: 
\begin{equation}
\int\int\limits_{v_j}\int  \frac{\partial }{\partial x} {\frac{1}{{R_1}_{ij}}} dv_j =
\Bigg|\Bigg|\Bigg| 
y \ln(z + {R_1}) + z \ln(y + {R_1}) -  x  \tan^{-1} \Bigg( \frac{yz}{x \:{R_1}} \Bigg) 
\Bigg|_{x_1}^{x_2} \Bigg|_{y_1}^{y_2} \Bigg|_{z_1}^{z_2}
\label{dx1}
\end{equation}
\begin{equation}
\int\int\limits_{v_j}\int  \frac{\partial }{\partial y} {\frac{1}{{R_1}_{ij}}} dv_j =
\Bigg|\Bigg|\Bigg|
x \ln(z + {R_1}) + z \ln(x + {R_1}) -  y  \tan^{-1} \Bigg( \frac{xz}{y \:{R_1}} 
\Bigg)
\Bigg|_{x_1}^{x_2} \Bigg|_{y_1}^{y_2} \Bigg|_{z_1}^{z_2}
\label{dy1}
\end{equation}
\begin{equation}
\int\int\limits_{v_j}\int  \frac{\partial }{\partial z} {\frac{1}{{R_1}_{ij}}} dv_j =
\Bigg|\Bigg|\Bigg|
x \ln(y + {R_1}) + y \ln(x + {R_1}) -  z  \tan^{-1} \Bigg( \frac{xy}{z \:{R_1}} \Bigg) 
\Bigg|_{x_1}^{x_2} \Bigg|_{y_1}^{y_2} \Bigg|_{z_1}^{z_2}
\label{dz1}
\end{equation}
For simplicity,  we omit the subscripts $i$ and $j$ in equations \ref{dx1} $-$ \ref{dz1}; hence, the variables $x$, $y$ and $z$  are relative coordinates of the $i$th point of the displacement referred to the coordinates to the corner of the $j$th prism modeling the reservoir, i.e.,  $x = x_j - x_i $, $\: y = y_j - y_i $, $\: z = z_j - z_i $ and 
$\: {R_1} = \sqrt{x^{2} + y^{2} + z^{2}}$.
In equations \ref{dx1} $-$ \ref{dz1}, the limits of the integrals represent the borders of the $j$th prism modeling the reservoir in the following way: $x_1$ and $x_2$ are their south and north borders; $y_1$ and  $y_2$ are their  west and east borders;  and 
$z_1$ and $z_2$ are their depths to the top and bottom.
\cite{Nagyetal2000} and (\citeyear{Nagyetal2002}) provided limit values of integrals shown in equations \ref{dx1} $-$ \ref{dz1} when the computation point coincides with the corner of the prism.

>>>>

From the potential theory, a particular solution of equation \ref{eq:poisson} is
\begin{equation}
\phi(x,y,z) = -  \frac{m}{4 \pi} \int\int\limits_{v}\int \frac{T(x^{\prime}, y^{\prime}, z^{\prime} )}{\sqrt{(x - x^{\prime})^{2} + (y - y^{\prime})^{2} + (z - z^{\prime})^{2}}} \: dv^{\prime},
\label{eq:phi}
\end{equation}
where $\phi(x,y,z)$ represents the Newtonian gravitational potential \citep{Kellogg29} that would be produced at the coordinates $x, y$ and $z$ by a continuous density distribution $- \frac{m}{4 \pi}  \: T( x^{\prime}, y^{\prime}, z^{\prime} )$. 
The integral in equation \ref{eq:phi} is conducted over the coordinates $x^{\prime}$,$y^{\prime}$ and $z^{\prime}$, denoting, respectively, the $x-$, $y-$ and $-z$ coordinates of an arbitrary point belonging to the interior of the volume $v$ of the solid.

@@

\: \Delta p_{j} \: \:dv_j^{\prime}

@@

\phi_{1} = - \frac{C_m}{4 \pi}  \frac{\Delta p_{j} \: \:dv_j^{\prime}}{ {R_1}_{ij} } \: .

@@

\bigg]   \: \Delta p_{j}  \:dv_j^{\prime}

@@

\phi_{2} = - \frac{C_m}{4 \pi}  \frac{\Delta p_{j} \: \:dv_j^{\prime}}{ {R_2}_{ij} } \: .

@@

$\Delta p_j$  is the pressure contrast of the $j$th nucleus, $dv_j^{\prime}$ is an 
infinitesimal element of volume centered at the $j$th nucleus of strain 
$(x^{\prime}_{j}, y^{\prime}_{j}, z^{\prime}_{j})$, $A$ is the constant

@@

\: \Delta p_{j} \: \:dv_j^{\prime} \: .

@@

By following \cite{Sharma56} and \cite{Tempone10}, 
the stress vector 
$\mbox{\boldmath$\sigma$}_{ij} \equiv \mbox{\boldmath$\sigma$}(x_{i}, y_{i}, z_{i}, x^{\prime}_{j}, y^{\prime}_{j}, z^{\prime}_{j})$ 
at the point $(x_{i}, y_{i}, z_{i})$ due to the $j$th single nucleus of strain buried 
in the half space is given by
\begin{equation}
\mbox{\boldmath$\sigma$}_{ij} = \mbox{\boldmath$\sigma_{1}$}_{ij} + 
\mbox{\boldmath$\sigma_{2}$}_{ij} \: ,
\label{eq:stress_nucleus}
\end{equation}
where 
$\mbox{\boldmath$\sigma_{1}$}_{ij} \equiv \mbox{\boldmath$\sigma_{1}$}(x_{i}, y_{i}, z_{i}, x^{\prime}_{j}, y^{\prime}_{j}, z^{\prime}_{j})$ is the stress vector 
at the point $(x_{i}, y_{i}, z_{i})$ due to the $j$th single nucleus in the infinite space and $\mbox{\boldmath$\sigma_{2}$}_{ij} \equiv \mbox{\boldmath$\sigma_{2}$}(x_{i}, y_{i}, z_{i}, x^{\prime}_{j}, y^{\prime}_{j}, z^{\prime}_{j})$ is the stress vector 
at the point $(x_{i}, y_{i}, z_{i})$ that gives the correction of the stress due to the 
$j$th image nucleus considering a semi-space. These two vectors are given by
\begin{equation}
\mbox{\boldmath$\sigma_{1}$}_{ij} =
A  \: 
\begin{bmatrix} 
\frac{\partial^{2} }{\partial x \partial z} {\frac{1}{{R_1}_{ij}}}  \\
\frac{\partial^{2} }{\partial y \partial z} {\frac{1}{{R_1}_{ij}}}  \\
\frac{\partial^{2} }{\partial z^{2}} {\frac{1}{{R_1}_{ij}}} 
\end{bmatrix}
\: \Delta p_{j} \: \:dv_j^{\prime} \: ,
\label{eq:nucleus-stress1-vector}
\end{equation}
and 
\begin{equation}
\mbox{\boldmath$\sigma_{2}$}_{ij} = 
A  \: 
\left\{
\begin{bmatrix} 
\frac{\partial^{2}  }{\partial x \partial z} {\frac{1}{{R_2}_{ij}}} \\
\frac{\partial^{2} }{\partial y \partial z} {\frac{1}{{R_2}_{ij}}} \\
- \frac{\partial^{2} }{\partial z^{2}} {\frac{1}{{R_2}_{ij}}}   
\end{bmatrix}
+ 2 \: z_{i}
\begin{bmatrix} 
\frac{\partial^{3}  }{\partial x \partial z^{2}} {\frac{1}{{R_2}_{ij}}} \\
\frac{\partial^{3} }{\partial y \partial z^{2}} {\frac{1}{{R_2}_{ij}}} \\
\frac{\partial^{3} }{\partial z^{3}} {\frac{1}{{R_2}_{ij}}} 
\end{bmatrix}
\right\}
\: \Delta p_{j} \: \:dv_j^{\prime} \: .
\label{eq:nucleus-stress2-vector}
\end{equation}
According to \cite{Sharma56} and \cite{Tempone10}, the Beltrami’s equations \citep{Beltrami} and the equilibrium equations must be satisfied to obtain the contribution of the stress field in the half space. 
Additionally, the following boundary conditions at the free surface ($z_i = 0$) 
must be satisfied
\begin{equation}
\mbox{\boldmath$\sigma$}_{ij} = \mbox{\boldmath$\sigma_{1}$}_{ij} + 
\mbox{\boldmath$\sigma_{2}$}_{ij} = \mbox{ \boldmath$0$},
\label{eq:null_stress}
\end{equation}
where $\mbox{ \boldmath$0$}$ is the null vector.
This condition can be easily verified by adding the vectors 
$\mbox{\boldmath$\sigma_{1}$}_{ij}$ (equation \ref{eq:nucleus-stress1-vector}) and 
$\mbox{\boldmath$\sigma_{2}$}_{ij}$ (equation \ref{eq:nucleus-stress2-vector}) 
computed at any point on the free surface $(x_i, y_i, z_i = 0)$.

@@

We parameterize the reservoir as a grid of juxtaposed right rectangular prisms.
Each grid prism has a constant pressure contrast $\Delta p_{j}$; however, pressure variations among different prisms are allowed. 
To calculate the displacement field produced by the $j$th prism
at the $i$th coordinates  $(x_i$, $y_i, z_i)$, we integrate the solution deduced for a single nucleus of strain (equation \ref{eq:displacement_ui})
over its volume and obtain
{\bf{\tilde{u}}}_{ij} = 
\iiint\limits_{{v_{1}}_{j}}
{\bf{u_{1}}}_{ij} \: \:  dv_{j}^{\prime}
\: + \:
\iiint\limits_{{v_{2}}_{j}}
{\bf{u_{2}}}_{ij} \:\:  dv_{j}^{\prime} \: ,
\label{eq:nucleus-ui_jth_prism}
where both integrals are conducted with respect to the variables $(x^{\prime}_{j}, y^{\prime}_{j}, z^{\prime}_{j})$, but the first is conducted over the volume ${v_{1}}_{j}$ of the $j$th prism and the second is conducted over the volume 
${v_{2}}_{j}$ of a different prism symmetrically positioned above the free surface 
and conveniently called $j$th "image prism".
Volume ${v_{1}}_{j}$ is defined by ${x_1}_{j}$, ${x_2}_{j}$, ${y_1}_{j}$, ${y_2}_{j}$,
${z_1}_{j}$, and ${z_2}_{j}$, which represent, respectively, the south, north, west, 
east, top, and bottom borders of the $j$th prism.
Volume ${v_{2}}_{j}$ of the $j$th image prism is defined in a similar way, but with 
top and bottom borders given by $z_1 - 2 \, z_c$ and $z_2 - 2 \, z_c$, where 
$z_c = \frac{1}{2}(z_1 + z_2)$ is the center depth of the $j$th prism.
By substituting equations \ref{eq:nucleus-u1-vector} and \ref{eq:nucleus-u2-vector} into equation \ref{eq:nucleus-ui_jth_prism}, we obtain
{\tilde{u}}_{{ij}_\alpha} = \frac{A  \: (1 + \nu)}{E} 
\: \Delta p_{j}  \: \left[ \iiint\limits_{{v_{1}}_{j}} 
\frac{\partial }{\partial \alpha} {\frac{1}{{R_1}_{ij}}} \:  dv_{j}^{\prime} 
\: + \: 
(3  - 4 \nu)  \iiint\limits_{{v_{2}}_{j}}
\: \frac{\partial }{\partial \alpha} {\frac{1}{{R_2}_{ij}}}\:  dv_j
+ \: 2 \: z_{i} \:  \iiint\limits_{{v_{2}}_{j}}
\frac{\partial^{2}  }{\partial \alpha \partial z} {\frac{1}{{R_2}_{ij}}}  \:\:  dv_{j}^{\prime} 
\right] \: , 
\label{eq:u_til_alpha}
where $\alpha = x, y$, and
{\tilde{u}}_{{ij}_z} = \frac{A  \: (1 + \nu)}{E} 
\: \Delta p_{j}  \: \left[ \iiint\limits_{{v_{1}}_{j}}
\frac{\partial }{\partial z} {\frac{1}{{R_1}_{ij}}} \:  dv_j 
\: - \: (3  - 4 \nu)  \iiint\limits_{{v_{2}}_{j}}
\: \frac{\partial }{\partial z} {\frac{1}{{R_2}_{ij}}}\:  dv_j
+ \: 2 \: z_{i} \:  \iiint\limits_{{v_{2}}_{j}}
\frac{\partial^{2}  }{\partial z^{2}} {\frac{1}{{R_2}_{ij}}}  \:\:  dv_j 
\right] \: .
\label{eq:u_til_z}
In the right-hand side of equations \ref{eq:u_til_alpha} and \ref{eq:u_til_z}, the three integrals have the same form of derivatives of the gravitational potential produced by the 
$j$th prism. 
The first integral corresponds to the $\alpha-$component of the gravitational attraction 
produced by the $j$th prism.
The second and third integrals correspond, respectively, to the $\alpha-$component of the gravitational attraction and to the $\alpha \:z-$component of the gravitational 
gradient tensor produced by the $j$th image prism. 
The similarity between the displacement fields due to a volume source in a half-space and the gravitational field allows the use of closed expressions of the gravitational potential and its derivatives produced by the 3D right rectangular prism.  
In equations  \ref{eq:u_til_alpha} and \ref{eq:u_til_z}, the integrals depending on 
first derivatives of ${\frac{1}{{R_1}_{ij}}}$ have the following closed solutions 
\citep{Nagyetal2000, Nagyetal2002}:
\int\limits_{{x_{1}}_{j}}^{{x_{2}}_{j}} \int\limits_{{y_{1}}_{j}}^{{y_{2}}_{j}} \int\limits_{{z_{1}}_{j}}^{{z_{2}}_{j}}
\frac{\partial }{\partial x} {\frac{1}{{R_1}_{ij}}} dv_{j}^{\prime} =
\Bigg|\Bigg|\Bigg| 
y \ln(z + {R_1}) + z \ln(y + {R_1}) -  x  \tan^{-1} \Bigg( \frac{yz}{x \:{R_1}} \Bigg) 
\Bigg|_{{X_1}_{j}}^{{X_2}_{j}} \Bigg|_{{Y_1}_{j}}^{{Y_2}_{j}} \Bigg|_{{Z_1}_{j}}^{{Z_2}_{j}} \quad ,
\label{dx1}
\int\limits_{{x_{1}}_{j}}^{{x_{2}}_{j}} \int\limits_{{y_{1}}_{j}}^{{y_{2}}_{j}} \int\limits_{{z_{1}}_{j}}^{{z_{2}}_{j}}
\frac{\partial }{\partial y} {\frac{1}{{R_1}_{ij}}} dv_{j}^{\prime} =
\Bigg|\Bigg|\Bigg|
x \ln(z + {R_1}) + z \ln(x + {R_1}) -  y  \tan^{-1} \Bigg( \frac{xz}{y \:{R_1}} 
\Bigg)
\Bigg|_{{X_1}_{j}}^{{X_2}_{j}} \Bigg|_{{Y_1}_{j}}^{{Y_2}_{j}} \Bigg|_{{Z_1}_{j}}^{{Z_2}_{j}} \quad ,
\label{dy1}
\int\limits_{{x_{1}}_{j}}^{{x_{2}}_{j}} \int\limits_{{y_{1}}_{j}}^{{y_{2}}_{j}} \int\limits_{{z_{1}}_{j}}^{{z_{2}}_{j}}
\frac{\partial }{\partial z} {\frac{1}{{R_1}_{ij}}} dv_{j}^{\prime} =
\Bigg|\Bigg|\Bigg|
x \ln(y + {R_1}) + y \ln(x + {R_1}) -  z  \tan^{-1} \Bigg( \frac{xy}{z \:{R_1}} \Bigg) 
\Bigg|_{{X_1}_{j}}^{{X_2}_{j}} \Bigg|_{{Y_1}_{j}}^{{Y_2}_{j}} \Bigg|_{{Z_1}_{j}}^{{Z_2}_{j}} \quad ,
\label{dz1}
where all derivatives are computed with respect to the coordinates of the $i$th point 
$(x_i, y_i, z_i)$, ${R_1} = \sqrt{x^{2} + y^{2} + z^{2}}$, and
\begin{array}{ll}
{X_1}_{j} &= x_i - {x_1}_{j} \\
{X_2}_{j} &= x_i - {x_2}_{j} \\
{Y_1}_{j} &= y_i - {y_1}_{j} \\
{Y_2}_{j} &= y_i - {y_2}_{j} \\
{Z_1}_{j} &= z_i - {z_1}_{j} \\
{Z_2}_{j} &= z_i - {z_2}_{j}
\end{array} \quad .
\label{eq:Nagy_solutions_1}

@@

For simplicity,  we omit the subscripts $i$ and $j$ in equations \ref{dx1} $-$ \ref{dz1}; hence, the variables $x$, $y$ and $z$  are relative coordinates of the $i$th point of the displacement referred to the coordinates to the corner of the $j$th prism modeling the reservoir, i.e.,  $x = x_j - x_i $, $\: y = y_j - y_i $, $\: z = z_j - z_i $ and 
$\: {R_1} = \sqrt{x^{2} + y^{2} + z^{2}}$.
In equations \ref{dx1} $-$ \ref{dz1}, the limits of the integrals represent the borders of the $j$th prism modeling the reservoir in the following way: $x_1$ and $x_2$ are their south and north borders; $y_1$ and  $y_2$ are their  west and east borders;  and 
$z_1$ and $z_2$ are their depths to the top and bottom.
\cite{Nagyetal2000} and (\citeyear{Nagyetal2002}) provided limit values of integrals shown in equations \ref{dx1} $-$ \ref{dz1} when the computation point coincides with the corner of the prism.
